
\tiny
\dirtree{%
    .1 Project .
    .2 Domain.
    .3 Core.
    .4 \textcolor{cyan}{Id.go}.
    .4 \textcolor{cyan}{Error.go}.
    .3 Event.
    .4 \textcolor{cyan}{Event.go}.
    .4 \textcolor{cyan}{EventDispatcher.go}.
    .3 Communication.
    .4 Repository.
    .5 \textcolor{cyan}{Comunicator.go}.
    .3 Task.
    .4 CommunicationMode.
    .5 \textcolor{blue}{CommunicationMode.go}.
    .5 \textcolor{blue}{UnknownError.go}.
    .4 ExecutionMode.
    .5 \textcolor{blue}{ExecutionMode.go}.
    .5 \textcolor{blue}{UnknownError.go}.
    .4 Host.
    .5 \textcolor{blue}{Host.go}.
    .5 \textcolor{blue}{InvalidHostError.go}.
    .4 Port.
    .5 \textcolor{blue}{InvalidPortError.go}.
    .5 \textcolor{blue}{Port.go}.
    .4 Repository.
    .5 \textcolor{cyan}{Save.go}.
    .4 Events.
    .5 \textcolor{blue}{TaskCreated.go}.
    .4 Service.
    .5 Creator.
    .6 \textcolor{blue}{Creator.go}.
    .5 Looper.
    .6 \textcolor{blue}{looper.go}.
    .6 \textcolor{red}{Errors.go}.
    .4 Status.
    .5 \textcolor{blue}{Status.go}.
    .5 \textcolor{blue}{UnknownError.go}.
    .4 Step.
    .5 \textcolor{blue}{Id.go}.
    .5 \textcolor{blue}{Vo.go}.
    .5 \textcolor{blue}{Step.go}.
    .5 \textcolor{blue}{InvalidSentenceLenghtError.go}.
    .4 \textcolor{blue}{Id.go}.
    .4 \textcolor{blue}{Task.go}.
    .2 Application.
    .3 Port.
    .4 in.
    .5 Task.
    .6 CreateTask.
    .7 \textcolor{blue}{Command.go}.
    .7 \textcolor{blue}{Handler.go}.
    .6 TaskCreated.
    .7 \textcolor{blue}{Handler.go}.
    .2 Adapter.
    .3 in.
    .4 ApiGrpc.
    .5 Controller.
    .6 \textcolor{blue}{TaskController.go}.
    .5 gen.
    .6 task.
    .7 \textcolor{purple}{task.pb.go}.
    .7 \textcolor{purple}{task\_grpc.pb.go}.
    .5 proto.
    .6 \textcolor{purple}{task.proto}.
    .5 \textcolor{blue}{ApiGrpc.go}.
    .3 out.
    .4 Persistence.
    .5 Adapters.
    .6 TaskAdapters.
    .7 TaskAdapters.
    .8 \textcolor{blue}{PersistAdapter.go}.
    .5 Migrations.
    .6 \textcolor{olive}{setup\_up\_migration.sql}.
    .6 \textcolor{olive}{setup\_down\_migration.sql}.
    .5 Models.
    .6 \textcolor{blue}{TaskDbModel.go}.
    .6 \textcolor{blue}{StepDbModel.go}.
    .3 inout.
    .4 EventDispatcher.
    .5 \textcolor{blue}{EventDispatcher.go}.
    .2 Bootstrap.
    .3 \textcolor{blue}{App.go}.
}
\normalsize

